R MINOS Lineplot Notebooks

### 2023-06-15 minos/outcomes/make_lineplots_all.Rmd
fixing lineplots notebook with relative imports and removing scrap ideas.

---
title: "R MINOS Lineplot notebooks noice"
output: html_document
date: "2023-05-20"
---

@@

```{r setup, include=FALSE}
library(reticulate)
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '../..')
knitr::knit_engines$set(python = reticulate::eng_python)
```

@@

```{r }
knitr::include_graphics("../../plots/baseline_all_child_uplift_SF_12_aggs_by_year.png", error=FALSE)
```

@@

```{r }
knitr::include_graphics("../../plots/baseline_poverty_child_uplift_SF_12_aggs_by_year.png", error=FALSE)
```

@@

```{r }
knitr::include_graphics("../../plots/baseline_living_wage_SF_12_aggs_by_year.png", error=FALSE)
```

@@

```{r }
knitr::include_graphics("../../plots/baseline_energy_downlift_SF_12_aggs_by_year.png", error=FALSE)
```

@@

```{r }
knitr::include_graphics("../../plots/all_five_combined_SF_12_aggs_by_year.png", error=FALSE)
```

>>>>

---
title: "R MINOS Lineplot Notebooks"
output: html_document
date: "2023-05-20"
---

@@

```{r setup, include=FALSE}
library(reticulate) # for python in Rmd. 
library(knitr)
require(here)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
knitr::knit_engines$set(python = reticulate::eng_python)
reticulate::use_condaenv("minos_conda", required = TRUE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_poverty_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_living_wage_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_energy_downlift_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "all_five_combined_SF_12_aggs_by_year.png"), error=FALSE)
```
